---
title: "Homework 6"
author: "Kirti Agrawal"
date: "14/11/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Answer 1 a
```{r}
d = data.frame(x = c(110.5, 105.4, 118.1, 104.5, 93.6, 84.1, 77.8, 75.6),
               y = c(5.755, 5.939, 6.010, 6.545, 6.730, 6.750, 6.899, 7.862))
plot(d$x, d$y, xlab = "plant height", ylab = "grain yield")
fit_d = lm(y ~ x, data = d)
abline(fit_d)
```
"Using the abline command we got the least square regression line and from the plot we can identify the curve does not lie within the points of the graph. Hence, this is not a good fit."

Answer1 b
"H0:B1 is equal to 0, using F test(ANOVA)"
```{r}
anova(fit_d)
```
"F statistics = 18.46 on 1 and 6 degree of freedom. The relationship between the plant height and grain yield is not zero.
H0:B1 is not equal to 0, using T test"
```{r}
summary(fit_d)
```
"T value = 12.036 & T statistics = -4.296
Same conclusion as the F test."

Answer1 c
"95% confidence interval for the intercept B0
B0^ = 10.137455
t = 2.447
s.e.(B0^) = 0.842265
95% confidence interval for the intercept B0 = 10.137455 + 2.447 * 0.842265 = 12.223745405
95% confidence interval for the intercept B0 = 10.137455 - 2.447 * 0.842265 = 8.051164595"
```{r}
confint(fit_d)
```

Answer1d
```{r}
coef(fit_d)[1]
coef(fit_d)["x"]
```
"linear regression line for this dataset is Y^ = 10.13746+(-0.03717469)X
Raw residual = 0.3624 "

Answer1 e
"estimate sigma^2 of the error variance sigma2 = 0.13132"

Answer 1 f
```{r}
M = predict(fit_d, newdata = data.frame(x = 100), interval = "confidence")
print(M)
```

Answer 1g
```{r}
N = predict(fit_d, newdata = data.frame(x = 100), interval = "prediction")
print(N)
```
"Prediction interval provided the wider range as compared to the confidence interval."

Answer 1h
```{r}
x = summary(fit_d)
print(x$r.squared)
```
"R^2 is 0.75, it means 75% of the variation in the grain yield is explained by the plant height."

Answer2a
```{r}
df = data.frame(x = c(1, 2, 3, 4, 5, 6, 7, 8, 9),
                y = c(-2.08, -0.72, 0.28, 0.92, 1.20, 1.12, 0.68, -0.12, -1.28))
plot(d$x, d$y)
```

Answer2b
```{r}
plot(resid(fit_d), d$y)
```

Answer2c
```{r}
plot(resid(fit_d), d$x)
```

Answer2d
```{r}
plot(resid(fit_d), fitted(fit_d))
```

Answer2e
"c & d is a meaningful fit, as the values are scattered randomly and no clusters of values found. And b & d have similar patterns and are clustered" 





